checkData

### 2023-08-22 analysis/checkData.Rmd
new prepare sample folders

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)
```
# Rename colums

@@

# Inspect journals data

@@

```{r}
d_journals <- d_journals %>%
  filter(`Are you piloting?` == "No") %>%
  select(-`Are you piloting?`)
```

Change two journal names entered incorrectly so they match names in sample.

```{r}
d_journals <- d_journals %>% mutate(`Journal Name` = fct_recode(`Journal Name`, 
                                         "MEMORY & COGNITION" = "Memory & Cognition",
                                         "JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
```

```{r}
d2 <- d_journals %>%
  mutate(
    sample_journal_prominent = `Journal Name` %in% journal_list_prominent$Journal,
    sample_journal_random = `Journal Name` %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )
```

```{r}
d_journals %>% 
  count(`Journal Name`) %>%
  filter(n > 2)
```

>>>>

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)
```

# Rename colums

@@

# Inspect journal's data

@@

```{r}
d_journals <- d_journals %>%
  filter(pilot == "No") %>%
  select(-pilot)
```

Adjust two journal names entered incorrectly so they match names in sample.

```{r}
d_journals <- d_journals %>% mutate(journal = fct_recode(journal, 
                                         "MEMORY & COGNITION" = "Memory & Cognition",
                                         "JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
```

```{r}
d_journals <- d_journals %>%
  mutate(
    sample_journal_prominent = journal %in% journal_list_prominent$Journal,
    sample_journal_random = journal %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )
```

```{r}
d_journals %>% 
  count(journal) %>%
  filter(n > 2)
```
